Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-08-12 tex/scam/sparsistency.tex
proof update

\begin{theorem} (Controlling false positives) \\
\label{thm:false_positive}
Suppose assumptions A1-A4 hold.

Suppose $\lambda_n \geq c s B \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
\]

@@

\begin{theorem} (Controlling false negatives) \\
\label{thm:false_negative}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.\\

Suppose $\lambda \leq c sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

Then, with probability at least $1 - \frac{1}{n}$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} 
we have the following result.
\begin{corollary}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\

Suppose 
$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

Then, for all large enough $n$, we have that with probability at least $1-\frac{1}{n}$:
\begin{align*}
\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S
\end{align*}

>>>>

\begin{theorem} (Controlling false positives) \\
\label{thm:false_positive}
Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$.

Suppose $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{12}{np}$, for all $k \in S^c$, and for all $i'=1,...,n$:
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|
\]

@@

\begin{theorem} (Controlling false negatives) \\
\label{thm:false_negative}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint. Let $\tilde{\sigma}$ denote $\max(\sigma, B)$.\\

Suppose $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^2 \tilde{\sigma} s^{5/2}$.

Suppose 
$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$, where $c$ is a constant dependent only on $b, c_1$.\\

Then, with probability at least $1 - \frac{C}{n}$ for some constant $C$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} 
we have the following result.
\begin{corollary}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
$\lambda = \Theta\big( s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np} \big) $. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.

Suppose 
$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^4 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$.

Then, for all large enough $n$, we have that with probability at least $1-\frac{C}{n}$:
\begin{align*}
\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S
\end{align*}

where $c,C$ are constants, possibly dependent on $b, c_1$.

### 2014-08-12 tex/scam/summary.tex
boundedness
proof update

Our main result is the following.
\begin{stheorem}
Suppose assumptions A1-A4 hold. Let $\{\hat{f}_i\}$ be any AC solution and
let $\{\hat{g}_k\}$ be any DC solution, both estimated with 
regularization parameter $\lambda$ scaling as
$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
Suppose in addition that
\begin{gather}
\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2
  np}\\
\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}}
  \log^2 2np}.
\end{gather}
Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$:
\begin{align*}
\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S.
\end{align*}

@@

This shows that variable selection consistency is achievable under
exponential scaling of the ambient dimension, $p = O(\exp(n^c))
for c<1$, as for linear models. The cost of nonparametric estimation is
reflected in the scaling with respect to $s=|S|$, which can grow only
as $o(n^{4/25})$.

>>>>

Our main result is the following.
\begin{stheorem}
Suppose assumptions A1-A4 hold. Let $\{\hat{f}_i\}$ be any AC solution and
let $\{\hat{g}_k\}$ be any DC solution, both estimated with 
regularization parameter $\lambda$ scaling as
$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
Suppose in addition that
\begin{gather}
\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2
  np}\\
\alpha_g^2/\tilde{\sigma} \geq c B^4 \sqrt{\frac{s^5}{n^{4/5}}
  \log^2 2np}.
\end{gather} 
where $\tilde{\sigma} \equiv \max(\sigma, B)$ and $c$ is a constant dependent only on $b, c_1$.

Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$:
\begin{align*}
\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S.
\end{align*}

@@

This shows that variable selection consistency is achievable under
exponential scaling of the ambient dimension, $p = O(\exp(n^c))$
for $c<1$, as for linear models. The cost of nonparametric estimation is
reflected in the scaling with respect to $s=|S|$, which can grow only
as $o(n^{4/25})$.
